### 2023-01-18 doc/manuscript/translocation.qmd
Update knowledge gaps using selection vocabulary

-   Potential knowledge gap/opportunity/selling point: For rescued populations to contribute to landscape-scale species recovery, the fitness benefits gained through selection should manifest beyond the natal environment, allowing for the long-term growth and persistence of incipient populations in novel environmental conditions. A unique attribute of this study is that we describe the genetic changes associated with evolutionary rescue, and combine repeated translocations of "rescued" populations, longitudinal surveys, mark-recapture analysis, and population modeling to demonstrate the capacity of "rescued" populations to persist across a landscape of disease. Thus, ER combined with translocations promotes the recovery of a species on the brink of disease-induced extinction. These results may have broad implications for the many species worldwide that are threatened with extinction by the emergence of novel diseases.

>>>>

-   Potential knowledge gap/opportunity/selling point: For rescued populations to contribute to landscape-scale species recovery, the fitness benefits gained through selection should manifest beyond the natal environment, allowing for the long-term growth and persistence of incipient populations in novel environmental conditions. In this study, we first document evidence of strong selection in host populations that are persisting with a deadly fungal pathogen, indicative that evolutionary rescue in response to previous pathogen invasion has occurred. We then repeatedly translocate these "rescued" populations to non-natal habitats on the landscape and use longitudinal surveys, mark-recapture analysis, and population modeling to demonstrate that "rescued" populations recover and persist across a landscape of disease. Thus, natural selection combined with translocations promotes the recovery of a species on the brink of disease-induced extinction. These results may have broad implications for the many species worldwide that are threatened with extinction by the emergence of novel diseases.
